Is this normal? A new projection pursuit index to assess a sample against a multivariate null distribution

### 2025-02-01 paper.qmd
Fixed labels and cluster label position in Fig 6

# when drawing I want to add clustering information
labels <- data.frame(
  x = c(seq(1960, 2020, length.out = 7),
        as.numeric(names(X_km$cluster))),
  label = c(seq(1960, 2020, length.out = 7),
        paste0("\n",X_km$cluster))
)
cluster_df <- as_tibble(X_km$cluster, rownames = "year") %>%
  add_column(variable = "num_precp_01")
p <- plot(weather_SCD_rescaled, type = "cell", n_digits = 0, continuous_rowname = 10, rotate_x = FALSE) +
  geom_text(data = cluster_df,
            mapping = aes(x = as.numeric(year),
                               y = variable, label = value,
                          color = as.factor(value)),
            size = 3, fontface = "bold",
            inherit.aes = F) +
  scale_color_manual(values = c("#201158", "#005260", "#007C46", "#999600", "#F9A391"),
                     guide = "none") +
  theme(
    #legend.position = "none",
        aspect.ratio = 0.5,
        text = element_text(size = 10)) +
  scale_x_continuous(breaks = seq(1960, 2020, 5),
                     labels = c(as.character(seq(60, 95, 5)),
                                "00", "05",
                                as.character(seq(10, 20, 5))))
ggsave("images/weather3.png", p, "png", bg = "white",
       width = 6, height = 3)
```

@@

Reproduction of the results from @MAYRHOFER2023, showing which cells have been identified as outlying by their Shapley Cell Detector algorithm. Red cells indicate values higher than expected, blue cells values lower than expected. For years that have been identified as outliers in our approach we show the cluster assignment at the top.
:::

>>>>

# when drawing I want to add clustering information
labels <- data.frame(
  x = c(seq(1960, 2020, length.out = 7),
        as.numeric(names(X_km$cluster))),
  label = c(seq(1960, 2020, length.out = 7),
        paste0("\n",X_km$cluster))
)
cluster_df <- as_tibble(X_km$cluster, rownames = "year") %>%
  add_column(variable = "clust")
weather_SCD_rescaled$phi <- cbind((rep(0, nrow(weather_SCD_rescaled$phi))), weather_SCD_rescaled$phi)
weather_SCD_rescaled$x_original <- cbind((rep(0, nrow(weather_SCD_rescaled$x_original))), weather_SCD_rescaled$x_original)
colnames(weather_SCD_rescaled$phi) <-
  c(".", "atmx", "atmn", 
         "nsm",
         "nheat", "p",
         "sunh",
         "nclear",
         "ncloud",
         "rh",
         "rhmx" ,
         "rhmn",
         "vwind",
         "vw60",
         "vwmx",
         "prc",
         "nprec")

cluster_df$variable <- "."
p <- plot(weather_SCD_rescaled, type = "cell", n_digits = 0, continuous_rowname = 10, rotate_x = FALSE) +
  geom_text(data = cluster_df,
            mapping = aes(x = as.numeric(year),
                               y = variable, label = value,
                          color = as.factor(value)),
            size = 3, fontface = "bold",
            inherit.aes = F) +
  scale_color_manual(values = c("#040404", "#55125D", "#A01975", "#E45358", "#F7AA2D"),
                       #c("#201158", "#005260", "#007C46", "#999600", "#F9A391"),
                     guide = "none") +
  theme(
    #legend.position = "none",
        aspect.ratio = 0.5,
        text = element_text(size = 10)) +
  scale_x_continuous(breaks = seq(1960, 2020, 5),
                     labels = c(as.character(seq(60, 95, 5)),
                                "00", "05",
                                as.character(seq(10, 20, 5))))
ggsave("images/weather3.png", p, "png", bg = "white",
       width = 6, height = 3)
```

@@

Reproduction of the results from @MAYRHOFER2023, showing which cells have been identified as outlying by their Shapley Cell Detector algorithm. Red cells indicate values higher than expected, blue cells values lower than expected. For years that have been identified as outliers in our approach we show the cluster assignment in the last row.
:::
